Spatial Reasoning and Statistical Graphics

### 2014-10-11 Paper/Draft1/TestingVisualAptitude.Rnw
Scale by variance changes

<<VisualAptitude-setup, fig.keep='all', cache=FALSE, echo=FALSE, eval=TRUE>>=
rm(list=ls())
wd <- getwd()

@@

\begin{figure}[htbp]\centering
\includegraphics[width=\textwidth]{fig-VisReasoningAnalysisCat}
\caption[Visual Aptitude Study Results]{Sample demographic characteristics compared with lineup score.}\label{fig:visualaptitudecat}
\end{figure}

>>>>

<<VisualAptitude-setup, fig.keep='all', cache=FALSE, echo=FALSE, eval=TRUE, message=F, warning=F>>=
rm(list=ls())
wd <- getwd()

@@

\begin{figure}[htbp]\centering
\includegraphics[width=\textwidth]{fig-VisReasoningAnalysisCat}
\caption[Visual Aptitude Study Results]{Sample demographic characteristics compared with lineup score. Sex (male), Calculus completion, and hours spent playing video games per week are all associated with a difference in lineup score. }\label{fig:visualaptitudecat}
\end{figure}
